---
title       : "Disk Measurements"
subtitle    : "Bias and Uncertainties from Coordinate-Based data"
author      : "mangei11"
job         : 
framework   : html5slides   # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Disk Measurements

Motivation
* Determine diameter, cross-sectional area, and coordinates of center location from small number of points on disk perimeter
* Prediction performance for a given number of noisy measurement points?
* Effect of the number of measurement points?
* Effect of the noise level in the measurements?

--- .class #id

## Example
```{r input, echo=FALSE}
rm(list=ls())
# hard wired constants
diam_true <- 2
center_true <- c(0,0)
set.seed(2323)
# input parameters
npnt <- 12
relsd <- 0.05
```
Given: `r npnt` measurement points, `r relsd*100`% noise 

```{r data_simulation, echo=FALSE,fig.asp=1, fig.height=10}
nboot <- 1
gendat <- function(n,relsd){
        sd <- diam_true*relsd
        phi <- matrix(runif(n*nboot, min=0, max=2.*pi),nrow=nboot)
        nx <- matrix(rnorm(n*nboot, sd=sd),nrow=nboot)
        ny <- matrix(rnorm(n*nboot, sd=sd),nrow=nboot)
        x <- center_true[1] + diam_true/2*cos(phi) + nx
        y <- center_true[2] + diam_true/2*sin(phi) + ny
        list(x=x, y=y)
        }
dat <- gendat(n=12, relsd=0.05)
plot(x=dat$x[1,], y=dat$y[1,], xlab="x", ylab="y", main="Data", col="red", pch=19, cex=2)
points(center_true[1],center_true[2], col="blue",pch=3,cex=2)
```

--- .class #id

## ShinyApp Functionality


Input parameters:
* Number of measurement points
* Noise (standard deviation of normal noise, relative to true disk diameter)

Output results:     
* Estimates of expected values, standard deviation, bias, rmse
* Histograms of simulated results

--- .class #id
## Equations for Estimation

Coordinates of center location:
$$\left(\hat{x}_c,\hat{y}_c\right) = \left(\frac{1}{n}\sum_{i=1}^{n}{x_i},\frac{1}{n}\sum_{i=1}^{n}{y_i}\right)$$
Disk Diameter:
$$\hat{d} = \frac{2}{n}\sum_{i=1}^{n}{\sqrt{\left(x_i-\hat{x}_c\right)^2
+\left(y_i-\hat{y}_c \right)^2} }$$
Center offset (true center $\left(x_c,y_c\right)$):
$$\hat{r}_c = \sqrt{\left(\hat{x}_c-x_c\right)^2
+\left(\hat{y}_c-y_c\right)^2} $$

--- . class #id

##  Simulations (for `r npnt` measurement points, `r relsd*100`% noise)
```{r nboot, echo=FALSE}
nboot <- 1000
```

Statistics based `r nboot` bootstrap simulations; results as {expectation, stdev, bias, rmse}

```{r histcalc, echo=FALSE}
# function to predict center location
center <- function(x,y){ c(mean(x),mean(y))}

# function to predicted the diameter from the x-y data
diam <- function(x,y){ 
        cent <- center(x,y)
        2 * mean(sqrt((x-cent[1])^2 + (y-cent[2])^2))
}

# function to predict the area relative to the true area
area_rel <- function(diam){ diam^2/diam_true^2 } 

# distance between true and predicted center location
dist_center <- function(center) { sqrt( sum( (center-center_true)^2) )}

# simulation and analysis function 
resvecall <- function(n,relsd){
        dat <- gendat(n, relsd)
        cent1 <- center(dat$x[1,],dat$y[1,])
        for (i in 1:nboot){
                cent <- center(dat$x[i,],dat$y[i,])
                d <- diam(dat$x[i,],dat$y[i,])
                a <- area_rel(d)
                dist <- dist_center(cent)
                resi <- data.frame(diameter=d/diam_true, 
                                   area=a, dcenter=dist/diam_true)
                if (i == 1) {
                        statdat <- resi
                } else {
                        statdat <- rbind(statdat,resi)
                }
        }
        # compute mean, standard deviation, and bias
        means <- sapply(statdat,mean)
        sdev <- sapply(statdat, sd)
        bias <- means - c(1, 1, 0) 
                # subtract the true values from the means
        rmse <- sqrt(sdev^2+bias^2)
        list(x1=dat$x[1,], y1=dat$y[1,], simdat = statdat, 
                means=as.list(means), sdev=as.list(sdev), 
                bias = as.list(bias), rmse = as.list(rmse))
}
res <- resvecall(n=12, relsd=0.05)
``` 

* Rel. Diameter $D/D_{true}:$ {`r round(res$means$diameter,3)`, `r round(res$sdev$diameter,3)`, `r round(res$bias$diameter,3)`, `r round(res$rmse$diameter,3)`}
* Rel. Offset $r/D_{true}:$ {`r round(res$means$dcenter,3)`, `r round(res$sdev$dcenter,3)`, `r round(res$bias$dcenter,3)`, `r round(res$rmse$dcenter,3)`}

```{r histplot, echo=FALSE, fig.width=11, fig.height=5}
res <- res
par(mfrow = c(1,2)) #, mar = c(5,4,2,1))
hist(res$simdat$diameter, xlab="relative diameter", 
                     main="Diameters")
hist(res$simdat$dcenter, xlab="relative distance", 
                     main="Center-Offset Distances")
```
